---
title: "Public Speech AI"
author: "Timothy A. Model"
institute: "Miami University"
date: "7/15/2020"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      ratio: '16:9'
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyr)
library(quanteda)
library(pals)
library(tidytext)
library(xaringanthemer)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
style_mono_accent(
  base_color = "#57669E",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  text_font_size = "1.5rem",
  text_slide_number_font_size = "0.5em",
  header_h2_font_size = "1.75rem",
  extra_css = list("caption" = list("font-size" = "150%"))
)
```

```{css, echo=FALSE}
@media print {
  .has-continuation {
    display: block;
  }
}
```

## Public speaking is challenging! Public Speech AI can help!

Preparation is the key to speechwriting success.

Public Speech AI: an indispensable tool in the speechwriting toolkit. 

Leveraging unstructured textual speech data to inform speech writers and public speakers about:

1. Thematic clarity
2. Persuasiveness
3. Audience
4. Alliteration
5. Sentence variation
6. Word usage

---

## Thematic Clarity in Donald Trump's State of the Union Addresses

```{r trumpnet, fig.align="center", warning=FALSE, comment=FALSE, echo=FALSE, message=FALSE, dev='svg', fig.height=5.5}
trump <- readtext::readtext("Analysis/TrumpVsPutin/trump_sotu/*.txt")

trump_corpus <- corpus(trump$text)

trumptoks <- trump_corpus %>%
  tokens(remove_punct = TRUE,
         remove_numbers = TRUE,
         remove_symbols = TRUE) %>%
  tokens_tolower() %>%
  tokens_replace(c("americans", "america's"), 
                 c("american", "america")) %>% 
  tokens_remove(pattern = c(stopwords("english"),
                "thank", "you", "tonight", "applause",
                "can", "must", "much", "many", "united",
                "states", "two", "just",  "year", "like",
                "also", "finally", "come", "years", "ago",
                "want", "done", "now", "since", "get", 
                "every", "always", "ever", "time", "last",
                "know"),
                padding = FALSE)

trumpfcmat <- fcm(trumptoks, context = "window", tri = FALSE)
trumpfeat <- names(topfeatures(trumpfcmat, 40))
fcm_select(trumpfcmat, pattern = trumpfeat) %>%
  textplot_network(min_freq = 0.25,
                   edge_alpha = .6,
                   edge_color = "#f4a582",
                   vertex_size = 1,
                   vertex_labelsize = 5
                   )
```

---

## Thematic Clarity in Vladimir Putin's Addresses to the Federal Assembly

```{r putinnet, fig.align="center", warning=FALSE, comment=FALSE, echo=FALSE, message=FALSE, dev='svg', fig.height=5.5}
putin <- readtext::readtext("Analysis/TrumpVsPutin/putin_address/*.txt")

putin_corpus <- corpus(putin$text)

putin <- readtext::readtext("Analysis/TrumpVsPutin/putin_address/*.txt")
putintoks <- putin_corpus %>%
  tokens(remove_punct = TRUE,
         remove_numbers = TRUE,
         remove_symbols = TRUE) %>%
  tokens_tolower() %>%
  tokens_replace(c("russia's", "economic"), 
                 c("russia", "economy")) %>% 
  tokens_remove(pattern = c(stopwords("english"),
                            "make", "next", "must", "time",
                            "even", "can", "know", "now",
                            "also", "every", "need", 
                            "including", "like", 
                            "today", "want",
                            "important", "say", "well",
                            "years", "just", "year",
                            "let", "many", "necessary",
                            "see", "already",
                            "use", "take", "said"),
                padding = FALSE)

putinfcmat <- fcm(putintoks, context = "window", tri = FALSE)
putinfeat <- names(topfeatures(putinfcmat, 40))
fcm_select(putinfcmat, pattern = putinfeat) %>%
  textplot_network(min_freq = 0.25,
                   edge_alpha = .6,
                   edge_color = "#a6cee3",
                   vertex_size = 1,
                   vertex_labelsize = 5
  )
```

